
\section{Conclusions}
\label{sec:concl}

In this paper, we set out to find an optimal fantasy baseball lineup given players with auction prices and points produced and being constrained to budget. DraftKing found an incredible lineup that included well above average points for both hitters and pitchers. The number of generations was capped at $500$, which means that a slightly better lineup could have been accomplished given more time. The “optimal" lineup we found was a lineup found in hindsight. With the prices being from before the 2021 season and the points based off of 2021 stats, people actually drafting these players at these prices would not have the information we were given. Additionally, this is an optimal lineup if a manager of a fantasy baseball team was required to keep all of the players for the entire season. In reality, many leagues allow managers to trade, release, and add players throughout the season. This means that players who had incredible first parts of the season but then got injured might not be included in lineups, but would definitely be owned by real fantasy baseball managers. With all of this in mind, an interesting extension would be to look at the optimal lineup as the season progressed, allowing for changes in the roster. However, this would need stats from every player for every day of the $162$ game season, which unfortunately might not be entirely feasible. Given the stats and prices available to us, we believe we can and did find value in players that was not expected heading into the season and showed some players that exceeded all expectations.